Price of Anarchy for Mean Field Games

### 2018-08-03 PoA.tex
minor edit Theorem 2
avoid saying unecessary assumption

	Suppose now that $PoA =1$. Then $u_t = w_t$ for all $t \in [0,T]$ and clearly:
	$$D^u = u_T = w_T = D^w.$$
	Now, if we take the difference between the two Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), and by using $u_t = w_t$ for all $t \in [0,T]$, we obtain:
	\begin{equation}
		2 (A^u - A^w) w_t = C^u - C^w, \quad \forall \  t \in [0,T].
	\label{eq:wt=constant}
	\end{equation}
	Since $2(A^u - A^w) = \bar{b}_1$, in the case when $\bar{b}_1 =0$ we must have $C^u = C^w$. Otherwise, equation (\ref{eq:wt=constant}) implies that $u_t = w_t = (C^u - C^w) / \bar{b}_1 $, which are constants for all $t \in [0,T]$. Thus, the time derivatives of $u_t$ and $w_t$ should be zero. From equation (\ref{eq:riccati_ut_sol_deriv}), and the fact that $\delta_u^+ - \delta_u^- > 0$, we deduce: 
	$$ B (D^{u})^2 + 2 A^u D^u - C^u = 0.$$
	Similarly we also have $B (D^{w})^2 + 2 A^w D^w - C^w = 0$.

@@

The results show various limiting behaviors, such as some of the cases proved in the previous section. In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed. The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$. Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}. For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$. When there is full interaction or only interaction through the controls, then $\bar{b}_2>0$ and we see that $\lim_{b_2 \to 0}PoA>1$. For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$. Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is thus an unnecessary assumption. For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$. Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is thus an unnecessary assumption. This agrees with the conclusion of Remark \ref{remark_6}. Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.

>>>>

	Suppose now that $PoA =1$. Then $u_t = w_t$ for all $t \in [0,T]$ and clearly:
	$$D^u = u_T = w_T = D^w.$$
	Now, if we take the difference between the two Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), and by using $u_t = w_t$ for all $t \in [0,T]$, we obtain:
	\begin{equation}
		2 (A^u - A^w) w_t = C^u - C^w, \quad \forall \  t \in [0,T].
	\label{eq:wt=constant}
	\end{equation}
	Since $2(A^u - A^w) = \bar{b}_1$, in the case when $\bar{b}_1 =0$ we must have $C^u = C^w$. Otherwise, equation (\ref{eq:wt=constant}) implies that $u_t = w_t = (C^u - C^w) / \bar{b}_1 $, are constant for all $t \in [0,T]$. Thus, the time derivatives of $u_t$ and $w_t$ should be zero. From equation (\ref{eq:riccati_ut_sol_deriv}), and the fact that $\delta_u^+ - \delta_u^- > 0$, we deduce: 
	$$ B (D^{u})^2 + 2 A^u D^u - C^u = 0.$$
	Similarly we also have $B (D^{w})^2 + 2 A^w D^w - C^w = 0$.

@@

The results show various limiting behaviors, such as some of the cases proved in the previous section. In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed. The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$. Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}. For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$. When there is full interaction or only interaction through the controls, then $\bar{b}_2>0$ and we see that $\lim_{b_2 \to 0}PoA>1$. For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$. Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is therefore a sufficient, but not necessary, assumption. For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$. Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is therefore a sufficient, but not necessary, assumption. This agrees with the conclusion of Remark \ref{remark_6}. Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
